Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-10-30 demystify.tex
updates

\subsection{Interpreting Response}\label{sec:interpreting-response}
Even if you do everything right, you will likely get a generic (\autoref{sec:interpreting-response}) or no response from a prof. Don't take it personally. They might not have the bandwidth to take on new students (very common), or they might not be interested in your background.

@@

Profs. are busy. They have many deadlines, meetings, and emails, many of which are from prospective students looking for research opportunities. They also have a life outside of work, e.g., family, hobbies, etc.

But this is not why they ``ghost'' you and provide no response.  It is because they are trying to avoid misunderstandings.  A response, no matter how generic, might be misinterpreted by the student.  For example, if they say they are not taking students but still (strongly) encourage you to apply, the student might take it as a positive sign of admission. Or if they say they are not interested, the student might take it as a personal rejection. So it is safer to not reply at all to avoid misunderstandings.

>>>>

\subsection{Interpreting Response}\label{sec:interpreting-response}
Even if you avoid the kiss of death emails (\autoref{sec:kiss-of-death-emails}), you might still not get a reply.  This is very common and you should not take it personally.  There are many reasons why you might not get a reply, e.g., the prof. is not interested, they are too busy (\autoref{sec:busy}), they are not taking students, they are on vacation, etc.  Here are some common responses and what they mean:

@@

Profs. are busy. We have many deadlines, meetings, and emails, many of which are from prospective students looking for research opportunities. we also have a life outside of work, e.g., family, hobbies, etc.

However, this is not why we ``ghost'' you and provide no response.  It is because we want to avoid misunderstandings.  A response (\autoref{sec:interpreting-response}), no matter how clear we think it is, might be misinterpreted by the student.  For example, if we say we are not taking students but still (strongly) encourage to apply, then the student might take it as a positive sign of admission. Or if we say we are not interested, the student might take it as a personal rejection and not apply at all.  So it is not because we are too busy to reply, but because we do not want misunderstandings and have to deal with them later.
